% Shreyas' Curriculum Vitae
% Updated 10th April, 2017
% Author: Shreyas Vinod
% Email: shreyas@shreyasvinod.me

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT SETUP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{article}

% ESSENTIALS

\def \mytitle{Shreyas Vinods' Curriculum Vitae}
\def \myname{Shreyas Vinod}
\def \myemail{shreyas@shreyasvinod.me}
\def \myweb{https://shreyasvinod.me}
\def \myphone{+48 570 898 920}
\def \mygithub{https://github.com/servertech}
\def \mygitname{servertech}
\def \mylinkedin{https://linkedin.com/in/shreyasvinod}
\def \mylinkedinname{shreyasvinod}

\def \mykeywords{
  shreyas,
  vinod,
  shreyas vinod,
  resume,
  curriculum,
  vitae,
  curriculum vitae
}

% END ESSENTIALS

\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Use Garamond (gael-varoquaux.info/science/garamond-fonts-for-latex.html)
% Find \garamond in the file to enable/disable use.

\usepackage{garamond}

\usepackage{calc}
\usepackage{changepage}

\reversemarginpar

\usepackage[
  paper=a4paper,
  marginparwidth=30.5mm,
  marginparsep=1.5mm,
  margin=20mm,
  includemp
]{geometry}

\setlength{\parindent}{0cm}

\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}

% FOOTER

\lfoot{
  \hspace{\footpageshift}
  \parbox{4in}{\, \hfill
  \scriptsize \garamond Last updated on \today \ungaramond
  ~ \textbullet ~
  \scriptsize \garamond Typeset in \LaTeX \ungaramond
  \hfill \, \arabic{page} of \protect\pageref*{LastPage}}
}

% END FOOTER

\usepackage{xcolor,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{
  colorlinks,breaklinks,
  linkcolor=darkblue,urlcolor=darkblue,
  anchorcolor=darkblue,citecolor=darkblue,
  unicode,
  pdftitle={\mytitle},
  pdfauthor={\myname},
  pdfkeywords={\mykeywords}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HELPER COMMANDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The section headings
%
% Usage: \section{section name}

\renewcommand{\section}[1]{\pagebreak[3]%
  \hyphenpenalty=10000%
  \vspace{1.3\baselineskip}%
  \phantomsection\addcontentsline{toc}{section}{#1}%
  \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
  \vspace{-\baselineskip}\par}

% An itemize-style list with lots of space between items

\newenvironment{outerlist}[1][\quad\textbullet]%
  {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
  \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section

\newenvironment{lonelist}[1][\quad\textbullet]%
  {\begin{list}{#1}{%
  \setlength{\partopsep}{0pt}%
  \setlength{\topsep}{0pt}}}
  {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items

\newenvironment{innerlist}[1][\quad\textbullet]%
  {\vspace{3mm}\begin{itemize}[
    #1,leftmargin=*,parsep=0pt,itemsep=1pt,topsep=0pt,partopsep=0pt
  ]}
  {\end{itemize}\vspace{3mm}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section

\newenvironment{loneinnerlist}[1][\quad\textbullet]%
  {\begin{itemize}[
    #1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt
  ]}
  {\end{itemize}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HEADER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{adjustwidth}{-\marginparsep-\marginparwidth}{}
  {\Huge \garamond Shreyas Vinod}
  \hfill
  \begin{minipage}[b]{3.5cm}
    \flushbottom \flushleft \small \garamond
    ul. \.Zeromskiego 1/133 \\ \vspace{2pt}
    01-887 Warszawa, PL
  \end{minipage}
  \begin{minipage}[b]{4cm}
    \flushright \small \garamond
    \href{\mygithub}{\mygitname} \\ \vspace{2pt}
    \href{tel:\myphone}{\myphone} \\ \vspace{2pt}
    \href{\myweb}{\myweb} \\ \vspace{2pt}
    \href{mailto:\myemail}{\myemail}
  \end{minipage}
  \hspace{1mm}
  \begin{minipage}[b]{1.2cm}
    \flushleft \small \garamond \bfseries
    github \\ \vspace{2pt}
    phone \\ \vspace{2pt}
    web \\ \vspace{2pt}
    email
  \end{minipage}
\end{adjustwidth}

\begin{adjustwidth}{-\marginparsep-\marginparwidth}{}
  \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
    \rule{\columnwidth}{1pt}%
  \end{minipage}
\end{adjustwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Synopsis

\section{Synopsis}

{\garamond I revere the indefinite complexity of the universe and the human %
  mind. I have a quest -- to understand neural networks and their silicon %
  counterparts and a never-ending curiosity and passion for engineering and %
  robotics and a strong admiration for the field of Computer Science. %
  Understanding what gravity does is uninteresting. Why -- on the %
  other hand, must be beautiful.}

% Academia

\section{Academia}

{\garamond \href{https://www.pw.edu.pl/}
{\bfseries Politechnika Warszawska}, Warsaw, PL}
\hfill {\garamond \slshape 2015 -- present}
\begin{outerlist}
  \item[] {\garamond \slshape B.Sc., Computer Science \enskip %
            year 1 GPA: 4.4/5.0}
\end{outerlist}

% Programming

\section{Programming}

{\garamond C/C++ \textsl{(preferred: several ten thousand lines)}; Python; %
  Verilog; Java}

% Noteworthy Projects

\section{Noteworthy Projects}

{\garamond \href{https://github.com/ServerTech/elise}{\bfseries Elise}} 
\enskip {\garamond \slshape control automation for ROVs and multirotors on %
          embedded platforms}
\hfill {\garamond \slshape ongoing}
\begin{innerlist}
  \item {\garamond Designed for AHTI, an underwater ROV.}
  \item {\garamond Scalable and adaptable to multirotors and related %
          platforms.}
  \item {\garamond Multithreading capable to maximise performance of embedded %
          platforms.}
  \item {\garamond Handles a plethora of sensors, including inertial %
          measurement for PID control.}
  \item {\garamond Self-stabilisation and movement algorithms.}
  \item {\garamond Integral displacement calculation.}
\end{innerlist}

{\garamond \href{https://github.com/ServerTech/cortex}{\bfseries Cortex}}
\enskip {\garamond \slshape fast and lightweight bitboard UCI chess engine %
          in C++}
\hfill {\garamond \slshape December 2014}
\begin{innerlist}
  \item {\garamond Minimax with alpha-beta pruning.}
  \item {\garamond Uses processor-native 64-bit integers, or 'bitboards'.}
  \item {\garamond GCC's low level assembly: incredibly fast move generation.}
  \item {\garamond Move search efficiency using simple heuristics such as 
          MVV-LVA.}
  \item {\garamond Zobrist hashing and transposition tables for efficient %
          search.}
  \item {\garamond Simple, but effective static evaluation for roughly 2000 
          elo.}
  \item {\garamond Universal Chess Interface (UCI) GUI protocol supported.}
  \item {\garamond Intended to be upgraded to self-learning using dynamic %
          evaluation.}
\end{innerlist}

{\garamond \href{https://github.com/ServerTech/neptune}{\bfseries Neptune}}
\enskip {\garamond \slshape 16-bit custom RISC architecture microprocessor in %
          Verilog}
\hfill {\garamond \slshape October 2013}
\begin{innerlist}
  \item {\garamond Originally designed on a Xilinx Spartan 6 FPGA.}
  \item {\garamond Microcoded by hand atop a custom MIPS-like architecture.}
  \item {\garamond Handmade serial display segments with custom protocols.}
  \item {\garamond Human-readable instruction set.}
  \item {\garamond Intended to teach introductory assembly to fellow students.}
\end{innerlist}

\vspace{-3mm}

% Noteworthy Miscellaneous

\section{Noteworthy Miscellaneous}

{\garamond \href{https://www.marinetech.org/rov-competition-2/}%
  {\bfseries MATE Underwater Robotics Competition}, \slshape Long Beach, %
  CA, US}
\hfill {\garamond \slshape upcoming}
\begin{innerlist}
  \item {\garamond Team member of the \href{http://sknrp.meil.pw.edu.pl/}%
          {Students Underwater Robotics Association}.}
  \item {\garamond Responsible for control software, electronics and %
          automation.}
  \item {\garamond PID control from inertial measurement.}
  \item {\garamond Custom-built PCBs for power and sensors.}
  \item {\garamond Responsible for ROV control during the competition.}
\end{innerlist}

{\garamond%
  \href{%
  https://www.coursera.org/account/accomplishments/certificate/8QFCMALZAB}%
  {\bfseries An Introduction to Interactive Programming in Python}}
\hfill {\garamond \slshape November 2014}
\begin{outerlist}
\item[] {\garamond \slshape Rice University on Coursera, 100\%}
\end{outerlist}

% Interests

\section{Interests}

{\garamond Artificial Intelligence; machine learning; behavioural psychology; %
  philosophy; chess; writing; algorithmic, mathematical thinking; and %
  curiosity with a passion}

\newpage

% Professional

\section{Professional}

{\garamond \bfseries Freelance writing} \enskip {\garamond \slshape as a hobby}
\hfill {\garamond \slshape 2013 -- 2014}
\vspace{3mm}

{\garamond \href{https://hostus.us}{\bfseries HostUS}}
\enskip {\garamond \slshape web-hosting services}
\hfill {\garamond \slshape 2012}
\vspace{-1mm}
\begin{outerlist}
  \item[] {\garamond \slshape Systems Administrator}
  \vspace{-3mm}
  \begin{innerlist}
    \item {\garamond Systems administration during the company's genesis.}
  \end{innerlist}
  \vspace{-3mm}
\end{outerlist}

% Featured Blog Posts

\section{Featured ~~~ Blog Posts}

{\garamond \href{https://shreyasvinod.me/human-behavioural-psychology/}%
{\bfseries Human Behavioural Psychology and the Social Construct}}
\vspace{3mm}

{\garamond \href{https://shreyasvinod.me/the-egocentric-predicament/}%
{\bfseries The Egocentric Predicament: The Bad and the Atrocious}}

% Lingustics

\section{Linguistics}

{\garamond \href{https://www.ielts.org/}{\bfseries International English %
  Language Testing System (IELTS)}}
\hfill {\garamond \slshape November 2014}
\begin{outerlist}
  \item[] {\garamond \slshape Reading: 9.0 \enskip Listening: 9.0 \enskip %
            Writing: 7.5 \enskip Speaking: 8.5 \enskip Overall: 8.5}
\end{outerlist}
\vspace{3mm}

{\garamond \slshape Others: Hindi; Malayalam; and Marathi}

% Links

\section{Links}

{\garamond LinkedIn \enskip \href{\mylinkedin}{\slshape \mylinkedinname}}

% Personal

\section{Personal}

{\garamond Born \enskip \slshape 19 December, circa. 1997} \qquad
{\garamond Nationality \enskip \slshape Indian} \hfill
\vspace{3mm}

\end{document}